01_LH-SIP_Data_Reduction

### 2022-03-29 01_LH-SIP_Data_Reduction.Rmd
added assim efficiency calculations

---
title: "00_LH-SIP_Data_Reduction"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

@@

@@

>>>>

---
title: "01_LH-SIP_Data_Reduction"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

@@

## Load lipid d2H assimilation efficiency data

```{r}
d2H_assim <- read_xlsx("data/d2H_data_isotope_measurements.xlsx", sheet = 'lipids')
```

@@

## Reduce columns

```{r}
# Reduce the 0d --> 3d --> 7d incubation data
peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>% 
  mutate(time_course = "0d -->") %>%
  # Column reduction
  select(file_id,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         rel_area_FID,
         area_FID,
         d2H_mn_zero,
         d2H,
         at2H_mn_zero,
         F_0_at2H_se,
         at2H,
         area2_mn_zero,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         `2F_Me`,
         `2F_FAME`,
         `2F_alk`,
         F_label_mn,
         F_label_se,
         time_course
  ) %>% 
  # Turn all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  )

peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
  # Filter out 0d data points from this dataset
  filter(inc_time_d != 0) %>% 
  # Add a time course tag
  mutate(time_course = "3d -->") %>% 
  # Column reduction
  select(file_id,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         rel_area_FID,
         area_FID,
         d2H_mn_three,
         d2H,
         at2H_mn_three,
         F_0_at2H_se,
         at2H,
         area2_mn_three,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         `2F_Me`,
         `2F_FAME`,
         `2F_alk`,
         F_label_mn,
         F_label_se,
         time_course
  ) %>% 
  # Convert all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  )
```

# Assimilation efficiency

## Reduce data and get linear model

```{r}
d2H_assim_lm <- d2H_assim %>% 
  # Select columns of interest
  select(
    org_id,
    exp_id,
    Analyte,
    `Water dD`,
    `Lipid dD`
  ) %>% 
  drop_na() %>% 
  # Group by organism, experiment, analyte
  group_by(
    org_id,
    exp_id,
    Analyte
  ) %>% 
  # Filter out samples with three or fewer observations
  # (so that we can do a linear model)
  filter(n() > 3) %>% 
  tidyr::nest(
    data = c(`Water dD`, `Lipid dD`)
  ) %>% 
  mutate(
    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
    estimates = purrr::map(fit, broom::tidy),
    summary = purrr::map(fit, broom::glance)
  ) %>% tidyr::unnest(estimates)

# Simplify by only looking at the slopes
d2H_assim_lm_summary <- d2H_assim_lm %>% 
  filter(term == "`Water dD`")
```

# Export
```{r}
# Export as RDS
saveRDS(peaks_mapped_with_zeros_analytes_reduced,
        file = "cache/LH_SIP_data")

saveRDS(peaks_mapped_with_threes_analytes_reduced,
        file = "cache/LH_SIP_data_3d_onwards")

saveRDS(F_L_2F,
        file = "cache/heavy_label_data")

saveRDS(d2H_assim_lm_summary,
        file = "cache/d2H_assimilation")
```
